---
title: "rfcipSim (R FCIP Simulator)"

output:
  github_document:
    toc: true
    toc_depth: 3
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```



```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE,
                      echo = TRUE,
                        fig.path = "man/figures/")
library(knitr)
library(dplyr)
library(devtools)
load_all()
```

# Introduction
`rFarmPolicySim` provides tools to simulate U.S. farm-level revenue, revenue variability, and payment calculations under major federal farm programs. Supported programs include: 
    
- Federal Crop Insurance Program (FCIP)
- Noninsured Crop Disaster Assistance Program (NAP)
- Price Loss Coverage (PLC)
- Agricultural Risk Coverage (ARC)
- Ad-hoc disaster assistance programs
      
Users can run Monte Carlo experiments to evaluate program payments, subsidies, and election decisions under alternative policy scenarios

**Disclaimer:** This product uses data provided by the USDA, but is not endorsed by or affiliated with USDA or the Federal Government.

# Installation
`rFarmPolicySim` can be installed directly from github using `remotes::install_github("https://github.com/ftsiboe/rFarmPolicySim")`

# Supported Functionalities


