---
title: "Datasets"

output:
  github_document:
    toc: true
    toc_depth: 3
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
library(knitr)
library(dplyr)
library(devtools)
load_all()
```

# Datasets

This directory provides guidance on accessing the various datasets used in U.S. farm safety-net research. 

Please note that these datasets are based on gatherings from our past and ongoing research. They do not constitute an endorsement of any specific datasets, and we acknowledge that there are many other relevant datasets that may not be included here.

The datasets available via the `USFarmSafetyNetLab` package include:

  - [Contiguous county](https://github.com/ftsiboe/US-FarmSafetyNet-Lab/blob/main/data/contiguous_county.rda) `USFarmSafetyNetLab::contiguous_county`
  - [Index for price recived](https://github.com/ftsiboe/US-FarmSafetyNet-Lab/blob/main/data/index_for_price_recived.rda) `USFarmSafetyNetLab::index_for_price_recived`
  - [Marketing year average price](https://github.com/ftsiboe/US-FarmSafetyNet-Lab/blob/main/data/marketing_year_avg_price.rda) `USFarmSafetyNetLab::marketing_year_avg_price`
  - [RMA commodity type recodes](https://github.com/ftsiboe/US-FarmSafetyNet-Lab/blob/main/data/rma_type_recodes.rda) `USFarmSafetyNetLab::rma_type_recodes`
  - [FCIP demand instruments](https://github.com/ftsiboe/US-FarmSafetyNet-Lab/blob/main/data/fcip_demand_instruments.rda) `USFarmSafetyNetLab::fcip_demand_instruments`
  
Below are descriptions of each dataset and instructions on how to access them:

## Federal Crop Insurance Program (FCIP) – Summary of Business (SOB)

This dataset provides comprehensive participation information for the FCIP. It can be accessed via two methods depending on the period of analysis:

- **Available through the R package:**  
  - [rfcip](https://github.com/dylan-turner25/rfcip), which offers tools to retrieve SOB, COL, and reinsurance data at various levels of aggregation.
- **Download from this repository’s release assets:**  
   - [Summary of Business Releases](https://github.com/ftsiboe/US-FarmSafetyNet-Lab/releases/tag/sob)

## Federal Crop Insurance Program (FCIP) – Cause of Loss (COL)

This dataset offers summarized information on FCIP participation, segmented by different causes of loss. It can be accessed as follows:

- **Available through the R package:**  
  - [rfcip](https://github.com/dylan-turner25/rfcip).
- **Download from this repository’s release assets:**  
   - [Cause of Loss Releases](https://github.com/ftsiboe/US-FarmSafetyNet-Lab/releases/tag/col)

## Federal Crop Insurance Program (FCIP) – Reinsurance

This dataset provides reinsurance data for the FCIP
Available through the R package [**rfcip**](https://github.com/dylan-turner25/rfcip).

---
For questions or additional information about these datasets, please open an issue or contact us directly on GitHub.

## Examples in R

```{r examples, include=T}
# rfcip can be installed directly from github using remotes::install_github("https://github.com/dylan-turner25/rfcip")

# Example 1: Accessing SOB data via rfcip
sob1 <- rfcip::get_sob_data(year = 2020, crop = "corn")
head(tibble(sob1))

# Example 2: Accessing SOB data via this repository’s release assets
base_url <- "https://github.com/ftsiboe/US-FarmSafetyNet-Lab/releases/download"
version  <- "sob"
file <- "sobcov_2020.rds"
url <- paste(base_url, version, file, sep = "/")
sob2 <- tempfile(fileext = ".rds")
download.file(url, sob2, mode = "wb",quiet=TRUE)
sob2 <- readRDS(sob2)
head(tibble(sob2))

# Example 3: Accessing COL data via rfcip
col1 <- rfcip::get_col_data(year = 2020)
head(tibble(col1))

# Example 4: Accessing COL data via this repository’s release assets
version  <- "col"
file <- "colsom_2020.rds"
url <- paste(base_url, version, file, sep = "/")
col2 <- tempfile(fileext = ".rds")
download.file(url, col2, mode = "wb",quiet=TRUE)
col2 <- readRDS(col2)
head(tibble(col2))

# Example 5: Accessing Reinsurance data via rfcip
nationalSRA <- rfcip::nationalSRA
head(tibble(nationalSRA))
```
## 📚 Citation
If you find this repository useful, please star this project and cite our papers listed above.

See the [LICENSE](../LICENSE) file in the repository's root for details.

*Maintained by [ftsiboe](https://github.com/ftsiboe)*

