---
title: "Datasets"

output:
  github_document:
    toc: true
    toc_depth: 3
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
library(knitr)
library(dplyr)
library(devtools)
load_all()
```

# Datasets

This directory provides guidance on accessing the various datasets used in U.S. farm safety-net research. Below are descriptions of each dataset and instructions on how to access them:

## Federal Crop Insurance Program (FCIP) – Summary of Business (SOB)

This dataset provides comprehensive participation information for the FCIP. It can be accessed via two methods depending on the period of analysis:

- **Recent data (1989–present):**  
  Available through the R package [**rfcip**](https://github.com/dylan-turner25/rfcip), which offers tools to retrieve SOB, COL, and reinsurance data at various levels of aggregation.
- **Historical data (pre-1989):**  
  Download from this repository’s release assets:
  - [Historical summary of business by state, county, crop, and coverage](https://github.com/ftsiboe/US-FarmSafetyNet-Lab/releases/download/v0.1.0/historical_summary_of_business_by_state_county_crop_coverage.rds)
  - [Historical summary of business by state, county, and crop](https://github.com/ftsiboe/US-FarmSafetyNet-Lab/releases/download/v0.1.0/historical_summary_of_business_by_state_county_crop.rds)

```{r sob-examples, include=T}
# Example 1: Accessing SOB data via rfcip
# rfcip can be installed directly from github using remotes::install_github("https://github.com/dylan-turner25/rfcip")
df <- rfcip::get_sob_data(year = 2023)
# df <- rfcip::get_sob_data(year = 2015:2020, crop = "corn")
# df <- rfcip::get_sob_data(year = 2022, crop = c(41, 81), group_by = "state")

# Example 2: Accessing SOB data via this repository’s release assets
base_url <- "https://github.com/ftsiboe/US-FarmSafetyNet-Lab/releases/download"
version  <- "v0.1.0"
file <- "historical_summary_of_business_by_state_county_crop.rds"
url <- paste(base_url, version, file, sep = "/")
df <- tempfile(fileext = ".rds")
download.file(url, df, mode = "wb",quiet=TRUE)
df <- readRDS(df)
```

## Federal Crop Insurance Program (FCIP) – Cause of Loss (COL)

This dataset offers summarized information on FCIP participation, segmented by different causes of loss. It can be accessed as follows:

- **Recent data (1989–present):**  
  Available through the R package [**rfcip**](https://github.com/dylan-turner25/rfcip).
- **Historical data (pre-1989):**  
  Download from this repository’s release assets:
  - [Historical cause-of-loss indemnities with month](https://github.com/ftsiboe/US-FarmSafetyNet-Lab/releases/download/v0.1.0/historical_cause_of_loss_indemnities_with_month.rds)
  - [Historical cause-of-loss indemnities (aggregate)](https://github.com/ftsiboe/US-FarmSafetyNet-Lab/releases/download/v0.1.0/historical_cause_of_loss_indemnities_only.rds)
  - [Historical cause-of-loss premiums and indemnities](https://github.com/ftsiboe/US-FarmSafetyNet-Lab/releases/download/v0.1.0/historical_cause_of_loss_premimums_and_indemnities.rds)

```{r col-examples, include=T}
# Example 3: Accessing COL data via rfcip
# rfcip can be installed directly from github using remotes::install_github("https://github.com/dylan-turner25/rfcip")
df <- rfcip::get_col_data(year = 2020)
# df <- rfcip::get_col_data(year = 2019:2021)

# Example 4: Accessing COL data via this repository’s release assets
base_url <- "https://github.com/ftsiboe/US-FarmSafetyNet-Lab/releases/download"
version  <- "v0.1.0"
file <- "historical_cause_of_loss_premimums_and_indemnities.rds"
url <- paste(base_url, version, file, sep = "/")
df <- tempfile(fileext = ".rds")
download.file(url, df, mode = "wb",quiet=TRUE)
df <- readRDS(df)
```

## Federal Crop Insurance Program (FCIP) – Reinsurance

This dataset provides reinsurance data for the FCIP
Available through the R package [**rfcip**](https://github.com/dylan-turner25/rfcip).

```{r reinsurance-examples, include=T}
# Example 2:
# df <- rfcip::get_insurance_plan_codes()
# df <- rfcip::get_insurance_plan_codes(year = 2023, plan = "yp")
# df <- rfcip::get_insurance_plan_codes(year = 2023, plan = 1)
# df <- rfcip::get_insurance_plan_codes(year = 2023, plan = "yield protection")
# df <- rfcip::get_insurance_plan_codes(year = 2018:2022, plan = c("yp", "rp"))
```

---
For questions or additional information about these datasets, please open an issue or contact us directly on GitHub.


